---
title: "Metadata"
output:
  html_document:
    self_contained: false
params:
  author: NULL
  sample: NULL
  samplesheet: NULL
---


```{r setup, include=FALSE}
library(downloadthis)

knitr::opts_chunk$set(echo = TRUE)

Samplesheet <- params$samplesheet
Name <- params$author
Sample_Name <-params$sample
metadata <- read.csv(Samplesheet, header = TRUE)
names(metadata) <- sub("^X\\.", "", names(metadata))
names(metadata) <- sub("\\.", "", names(metadata))
m <- metadata[1, ]
m[ ] <- lapply(m, function(x) {
  if (is.character(x)) gsub('"', '', x) else x
}) 
```
  `r Sys.Date()` ---
**`r Name`** ---
**`r Sample_Name`** 


<style>
/* ==================================================================
CSS stylesheet adapted from boilerplate below: 
  CSS Boilerplate v2.0.2
  The Unlicense <https://unlicense.org>
  https://github.com/MattMcAdams/CSS-Boilerplate
================================================================== */

:root {

  /* Layout Widths */
  --width_content: 60rem; /* 960px + gutters */
  --width_sidebar: 20rem; /* 320px + gutters */
  --width_wide: calc(
    var(--width_content) +
    var(--width_sidebar) +
    var(--space_layout-gap)
  );
  /* Total wide width: 60rem + 20rem + 2rem = 82rem */

  /* Colors */
  --color_text--default: white;
  --color_text--subtle: #71717a;
  --color_text--link: #6366f1;
  --color_text--link-alt: #4f46e5;
  --color_text--accent: var(--color_text--link);
  --color_background--surface: black;
  --color_background--element: #f4f4f5;
  --color_background--chip: #e4e4e7;
  --color_accent: var(--color_text--link);


  /* Font Weights */
  --font_weight--thin: 100;
  --font_weight--extralight: 200;
  --font_weight--light: 300;
  --font_weight--normal: 400;
  --font_weight--medium: 500;
  --font_weight--semibold: 600;
  --font_weight--bold: 700;
  --font_weight--extrabold: 800;
  --font_weight--black: 900;
  --font_body : 'Verdana';

  /* Font Sizes & Line Heights */
  /* Based on a modular scale 1.125 by 1.2 */
  /* Exact values have been refined to be a whole pixel value */
  --font_size--small: 0.9375rem;    /* 15px */
  --font_size--normal: 1.125rem;    /* 18px */
  --font_size--medium: 1.375rem;    /* 22px */
  --font_size--large: 1.625rem;     /* 26px */
  --font_size--xlarge: 1.9375rem;   /* 31px */
  --font_size--xxlarge: 2.3125rem;  /* 37px */
  --font_size--xxxlarge: 2.8125rem; /* 45px */

  /* Line heights */
  --font_height--small: 1.2;
  --font_height--normal: 1.8;
  --font_height--medium: 1.5;
  --font_height--large: 1.3;
  --font_height--xlarge: 1.2;
  --font_height--xxlarge: 1.1;
  --font_height--xxxlarge: 1;
}

/* Medium font sizes */
/* Based on a modular scale 1.125 by 1.25 */
/* Exact values have been refined to be a whole pixel value */
@media (min-width: 30rem) {
  :root {
    --font_size--small: 0.875rem;     /* 14px */
    --font_size--medium: 1.4375rem;   /* 23px */
    --font_size--large: 1.75rem;      /* 28px */
    --font_size--xlarge: 2.1875rem;   /* 35px */
    --font_size--xxlarge: 2.75rem;    /* 44px */
    --font_size--xxxlarge: 3.4375rem; /* 55px */
  }
}

/* Large font sizes */
/* Based on a modular scale 1.125 by 1.3 */
/* Exact values have been refined to be a whole pixel value */
@media (min-width: 60em) {
  :root {
    --font_size--large: 1.875rem;     /* 30px */
    --font_size--xlarge: 2.5rem;      /* 40px */
    --font_size--xxlarge: 3.1875rem;  /* 51px */
    --font_size--xxxlarge: 4.1875rem; /* 67px */
  }
}

html, body, div, span, applet, object, iframe,
h1, h2, h3, h4, h5, h6, p, blockquote, pre,
a, abbr, acronym, address, big, cite, code,
del, dfn, em, img, ins, kbd, q, s, samp,
small, strike, strong, sub, sup, tt, var,
b, u, i, center,
dl, dt, dd, ol, ul, li,
fieldset, form, label, legend,
table, caption, tbody, tfoot, thead, tr, th, td,
article, aside, canvas, details, embed,
figure, figcaption, footer, header, hgroup,
menu, nav, output, ruby, section, summary,
time, mark, audio, video, hr {
  margin: 0;
  padding: 0;
  border: 0;
  font: inherit;
  font-size: 100%;
  vertical-align: baseline;
}

/* HTML5 display-role reset for older browsers */

article, aside, details, figcaption, figure,
footer, header, hgroup, menu, nav, section {
  display: block;
}

body {
  line-height: 1;
}



/* Set the document's default font, color, size, and line height */

body {
  font-family: var(--font_body);
  font-size: var(--font_size--normal);
  line-height: var(--font_height--normal);
  color: var(--color_text--default);
  background: var(--color_background--surface);
  accent-color: var(--color_accent);
}

/* Heading typography */

h1 {
    font-size: 28px;
    font-weight: 600;
    color: white;
    margin-bottom: 30px;
}

h2,
.util_txt--h2 {
  font-size: var(--font_size--xxlarge);
  line-height: var(--font_height--xxlarge);
}

h3,
.util_txt--h3 {
  font-size: var(--font_size--xlarge);
  line-height: var(--font_height--xlarge);
}

h4,
.util_txt--h4 {
  font-size: var(--font_size--large);
  line-height: var(--font_height--large);
}

h5 {
  font-size: var(--font_size--medium);
  line-height: var(--font_height--medium);
}

/* Set typography for small text */

small,
.util_txt--small {
  font-size: var(--font_size--small);
  line-height: var(--font_height--small);
}

/* Basic styles for inline semantics */

strong, b { font-weight: bold; }
em, cite, i, q { font-style: italic; }
s { text-decoration: line-through; }
u { text-decoration: underline; font-style: normal; }

/* Basic style for subscript and superscript text */

sub, sup {
  font-size: 75%;
  line-height: 0;
  position: relative;
}

sup { top: -0.5em; }
sub { bottom: -0.25em; }

del {
  background: var(--color_background--element);
  text-decoration: line-through;
  padding: 0.1em 0.3em;
}

ins {
  background: var(--color_background--element);
  text-decoration: underline;
  padding: 0.1em 0.3em;
}



/* CUSTOM CSS SETTINGS ADDED  */
.main-container {
    margin-left: 0;
    margin-right: 0;
    max-width: 1800px;
}

#map iframe {
  width: 100%;
  height: 100%;
}




.mainblocks {
    display: flex;
    margin-left: 1em;
    margin-right: 1em;
    margin-top: 1em; 
    margin-bottom: 1em
}

.sectiontitle {
    font-weight: bold;          
    text-align: center;         
    width: 100%;  
    border: none;
    color:black
}

#part1 {
    display: flex;
    flex-direction: column;
}
#part1content {
  display: flex;
  flex-direction: row; 
  justify-content: space-evenly;
  height: 30%;
  width: 100%;
}

#SI {
    background-color: #d284ffdf;

}
#left{
    display: flex; 
    flex-direction: column;
    width: 33.3%;
    background-color: #d9aaf532;
}

#right{
    width: 66.6%;
    background-color: #d9aaf532;
    padding-left:0.5%;
}

#map {
    display: flex;
    height: 66%;
    margin:0.5%;
}

#Sampleimage, #Samplename, #Species{
    align-self: center;
    border: none
}

#part3 {
  display: flex;
  flex-direction: row; 
  gap: 1%;
  border: none;
}

#Colltitle {
    background-color: aquamarine;
}
#Collection {
    background-color: rgba(127, 255, 212, 0.209);
}

#RNA {
    background-color: aquamarine;
}

#RNAExtraction {
    background-color: rgba(127, 255, 212, 0.209);

}

#Seq {
    background-color: aquamarine;
}

#QCSequencing {
    background-color: rgba(127, 255, 212, 0.209);
}

#Analy {
    background-color: aquamarine;

}
#Analysis {
    background-color: rgba(127, 255, 212, 0.209);
}


#Collection, #RNAExtraction, #QCSequencing, #Analysis {
 width: 24% 
}
#Collection {
    margin-left: 1%;
}
#Analysis {
    margin-right: 1%;
}



#DA {
    background-color: rgb(136, 241, 130);
}

#DataAvail {
    background-color: rgba(135, 241, 130, 0.224);

}


#DataAvail {
    display: flex;
    flex-direction: column;
}

#Notes {
    background-color: #f48bb327;
    display: flex; 
    flex-direction: column;
}
#N {
    background-color: #f48bb3;
}

#part6 {
    display: flex;
    flex-direction: row;
    justify-content: space-evenly;
    background-color: #afacb03a;
}

a {
  background: none !important;
  border: none !important;
  padding: 0 !important;
  color: white;   
  font-weight: normal;
}

a.hover {
  color: #23527c;
}

</style> 
<main class = "main-container" >
<div id="main">
<div class = "mainblocks" id="part1" > 
<div class = "sectiontitle" id = "SI"> Sample information</div>   
<div id = "part1content">
<div id="left"> 
<div id = "Samplename">`r m[["Sample_name"]]` </div>
<div id = "Sampleimage">

```{r, echo=FALSE, results='asis'}
image_url <- m$Image_path
img <- knitr::image_uri(image_url)
cat(sprintf(
  '<img src="%s" alt="Sample_image">',
  img
))
```

</div>
<div id = "Species">  <p> `r m[["Species"]]` </p>
</div>
</div>
<div id="right"> 
<div id = "LabsandAuthors"> 
<p id ="RawData"> Raw Data: <b> Lab: </b> `r m[["RawDatalab"]]`<b> ExpID:</b> `r m[["RawDataExpID"]]` <b> Author: </b> `r m[["RawDataAuth"]]` </p>
<p id ="Analysis "> Analysis:  <b> Lab: </b> <a href="mailto:`r m[["Contact_email"]]`"> `r m[["AnalysisDatalab"]]` </a> <b> ExpID:</b> `r m[["AnalaysisDataExpID"]]` <b> Author: </b> `r m[["AnalysisdataAuth"]]` </p>
</div>
<div id="map"> 
<iframe loading="lazy" style="width:100%; height:100%; border:0;" src="https://www.google.com/maps?q=`r m[["Lat"]]`,`r m[["Lon"]]`&z=5&output=embed">
 </iframe> 
</div>
</div>
</div>
</div>
<div class = "mainblocks" id = "Timeline" > 



</div>
<div class = "mainblocks" id="part3">
<div id = "Collection" > 
<div class = "sectiontitle" id = "Colltitle">Collection</div>   
<p id ="Origin"> <b> Origin: </b> `r m[["Origin"]]` </p>
<p id ="Source"> <b> Source: </b> `r m[["Source"]]` </p>
<p id ="Age"> <b> Age: </b> `r m[["Age"]]` </p>
<p id ="Sex"> <b> Sex: </b> `r m[["Sex"]]` </p>
<p id ="Size"> <b> Size: </b> `r m[["Size"]]` </p>
<p id ="Tissue"> <b> Tissue: </b> `r m[["Tissue"]]`</p>
<p id ="Tissuemass"> <b> Tissue mass: </b> `r m[["Tissue_mass"]]` </p>
<p id ="DateCollected"> <b> Date Collected: </b> `r m[["Collection_Date"]]` </p>
<p id ="Collected by"> <b> Collected by:  </b> `r m[["Collection_by"]]` </p>
<p id ="Storage"> <b> Storage:  </b> `r m[["Storage"]]` </p>
</div>
<div id = "RNAExtraction" > 
<div class = "sectiontitle" id = "RNA"  >RNA Extraction</div>   
<p id ="Homogenization"> <b> Homogenization: </b> `r m[["Homogenization_method"]]` </p>
<p id ="Extraction"> <b> Extraction Method: </b> `r m[["RNA_extraction_Method"]]` </p>
<p id ="Concentration"> <b> Concentration: </b> `r m[["Concentration"]]` </p>
<p id ="260280"> <b> 260/280: </b> `r m[["260.230"]]` </p>
<p id ="260230"> <b> 260/230: </b> `r m[["260.280"]]` </p>
<p id ="Date Extracted"> <b> Date Extracted: </b> `r m[["Extraction_date"]]` </p>
<p id ="Extraction by"> <b> Extraction by:  </b> `r m[["Extraction_by"]]` </p>       
</div>
<div id = "QCSequencing" > 
<div class = "sectiontitle" id = "Seq" > QC/Sequencing</div>   
<p id ="Date Submitted"> <b> Date Submitted: </b> `r m[["Sequence_Submission_Date"]]` </p>
<p id ="Sequencingby"> <b> Sequencing by : </b> `r m[["Sequencing_by"]]` </p>
<p id ="Sequencingorder "> <b> Order No: </b>`r m[["Submission_order_number"]]` </p>
<p id ="RIN"> <b> QC Method: </b> `r m[["QC_Method"]]` </p>
<p id ="RIN"> <b> RIN: </b> `r m[["RIN"]]` </p>
<p id ="Library_Prep"> <b> Library Prep: </b> `r m[["Library_Prep"]]` </p>
<p id ="Selection"> <b> Selection: </b> `r m[["Selection"]]` </p>
<p id ="layout"> <b> Library Layout: </b> `r m[["Library_Layout"]]` </p>
<p id ="Platform"> <b> Platform: </b> `r m[["Platform"]]` </p>
<p id ="ReadLength"> <b> Read length: </b> `r m[["Read_Length"]]` </p>
<p id ="Resultsrecevied by"> <b> Date received  </b> `r m[["Sequencing_Received_Date"]]` </p>
</div>
<div id = "Analysis" > 
<div class="sectiontitle" id = "Analy" > Analysis</div>   
<p id ="Trimming"> <b> Trimming tool: </b> `r m[["Preproccessing_tools"]]` </p>
<p id ="Trimmingby"> <b> Trimming by: </b> `r m[["Preprocessing_by"]]` </p>
<p id ="multiqc"> <b> Multiqc: </b> <a href="multiqc_report.html"> multiqc </a> </p>
<p id ="Assembler "> <b> Assembler: </b> `r m[["Assembler"]]` </p>
<p id ="Assembly by"> <b> Assembly by:  </b> `r m[["Trinity_Assembly_by"]]` </p>
<p id ="Analysisby"> <b> Analysis by:  </b> `r m[["Analysis_by"]]` </p>
</div>
</div>
<div class = "mainblocks" id = "DataAvail" >
<div class="sectiontitle" id = "DA"> Data Availability </div>   
<p id ="SRA"> <b> SRA: </b> `r m[["SRA"]]` </p>
<p id ="Access"> <b> Access: </b> `r m[["Access"]]` </p>
<p id ="Storage"> <b> Storage: </b> `r m[["Harddrive_Storage"]]` </p>
<p id ="PublishedDate"> <b> First Published: </b> `r m[["First_Published_Date"]]` </p>
<p id = "Publications"> <b> Related Publications: </b> `r m[["Related_Publications"]]` </p>
</div>
<div class = "mainblocks"  id = "Notes" >
<div class="sectiontitle" id = "N"> Notes </div>   
<p id ="notescontent"> `r m[["Misc_Notes"]]`</p>
</div>
<div class = "mainblocks" id="part6"> 
<div id = "Download" > 
```{r, results='asis', echo=FALSE}
metadata %>% 
  download_this(
    output_name = paste0(Sys.Date(), "_Metadata_", m$Sample_name[1]),
    output_extension = ".csv",
    button_label = "--- Download Metadata as csv ---",
    button_type = "default",
    csv2 = FALSE,
  )
```

</div>
</div>
</div>
</main>
