---
title: "Transcriptome Figures"
output: 
  html_document:
    css: style.css 
params:
  kallistotop20graphtrinity: NULL
  kallistotop500graphtrinity: NULL
  busco_figure1: NULL
  busco_figure2: NULL
  busco_figure3: NULL
  alluvial1P: NULL
  alluvial1L: NULL
  alluvial2P: NULL
  alluvial2L: NULL
  pie1: NULL
  pie2: NULL
  pie3: NULL
  pie4P: NULL
  pie4L: NULL
  topkallisto: NULL
  AuthorName: NULL
  SampleName: NULL
---
<style>
.table-hover > tbody > tr:hover {
  background-color: grey; 
}

caption {
  color: white;
  font-weight: bold;
}


</style>


```{r setup, include=FALSE,echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(repos = c(CRAN = "https://cran.rstudio.com"))

```

```{r, echo = FALSE, message=FALSE, warning= FALSE, results = 'hide'}
library(readr)
library(tidyr)
library(knitr)
library(gridExtra)
library(kableExtra)
library(png)
library(grid)
library(DT)
library(downloadthis)

```

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
kallistotop20graphtrinity <- params$kallistotop20graphtrinity
kallistotop500graphtrinity <- params$kallistotop500graphtrinity
alluvial1P <- params$alluvial1P
alluvial2P <- params$alluvial2P
alluvial1L <- params$alluvial1L
alluvial2L <- params$alluvial2L
pie1 <- params$pie1
pie2 <- params$pie2
pie3 <- params$pie3
pie4P <- params$pie4P
pie4L <- params$pie4L
topkallisto <- params$topkallisto
Sample_Name <- params$SampleName
Name <- params$AuthorName


```

<hr style="border: 1px solid white; width: 100%; margin:0px; padding:0px;" />

<!-- get current date --> 
`r Sys.Date()` ---
**`r Name`** ---
**`r Sample_Name`**  
<hr style="border: 1px solid white; width: 100%; margin:0px; padding:0px;" />

<div align="center">
### BUSCO  

```{r, results='asis'}
if (nchar(params$busco_figure1) > 0) {
  knitr::include_graphics(params$busco_figure1)
}
```

```{r, results='asis'}
if (nchar(params$busco_figure2) > 0) {
  knitr::include_graphics(params$busco_figure2)
}
```

```{r, results='asis'}
if (nchar(params$busco_figure3) > 0) {
  # Use busco_figure3
  knitr::include_graphics(params$busco_figure3)
}
cat(" \n\n Figure 1. BUSCO score of transcriptome(s). \n\n ") 

```

### Kallisto Distribution of Top 500 expressed transcripts 

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
Trinity_Top500_read <- readPNG(kallistotop500graphtrinity)
top500 <- grid.raster(Trinity_Top500_read)
cat("\n\n Figure 2. Kallisto Distribution of Top 500 expressed transcripts. Kallisto was run using the transcriptome file as an index and trimmomatic files as inputs with bootstraps.Y axis shows the transcript per million(tpm) counts per target id. X shows each target id (transcriptome sequence). \n\n") 

```

### Kallisto Distribution of Top 20 expressed transcripts 


```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
Trinity_Top200_read <- readPNG(kallistotop20graphtrinity)
top200 <- grid.raster(Trinity_Top200_read)
cat("\n\n Figure 3. Kallisto Distribution of Top 20 expressed transcripts. Kallisto was run using the transcriptome file as an index and trimmomatic files as inputs with bootstraps. Left Y axis shows the transcript per million(tpm) counts per target id. Right Y axis shows the cumulative percent of expression the top 20 most expressed transcripts. X shows each target id (transcriptome sequence). \n\n ") 
```

### % of Transcripts with a significant hit to a unitprot toxin
```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
P1 <- readPNG(pie1)
P1 <- grid.raster(P1)
cat("\n\n Figure 4. Pie chart showing the percentage of transcripts that showed a significant hit to annotated uniprot toxin. Blastx was done using the transcriptome file as the query and the annotated toxin database from uniprot as the database. Pie chart represents what percentage of distinct transcripts had at least one uniprot toxin match with a BitScore of at least 50. \n\n ") 
```


### Most significant uniprot toxin hit per transcript (BitScore >= 50)

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis',}
A1 <- readPNG(alluvial1P)
A1 <- grid.raster(A1)

A1L <- readPNG(alluvial1L)
A1L <- grid.raster(A1L)

cat("\n\n Figure 5. Alluvial graph representing the most significant uniprot toxin hit per transcript with at least one significant uniprot toxin hit. Significance threshold for this graph is a Bitscore of at least 50. On the right is each of the distinct transcripts with at least one significant uniprot toxin hit. One the left is are the uniprot toxin hits.  The coloured lines connecting the right bar to left indicate which hit was most significant for each transcript. (Note:if the bar on the right is completely black in colour, this indicates that there were simply too many transcripts to display. \n\n ") 
```

### Most significant uniprot toxin hit per transcript (BitScore >= 250)

<div style="background-color: white; padding: 10px;">

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}

A2 <- readPNG(alluvial2P)
A2 <- grid.raster(A2)

A2L <- readPNG(alluvial2L)
A2L <- grid.raster(A2L)
cat("\n\n Figure 6. Alluvial graph representing the most significant uniprot toxin hit per transcript with at least one significant uniprot toxin hit. Significance threshold for this graph is a Bitscore of at least 250. On the right is each of the distinct transcripts with at least one significant uniprot toxin hit. One the left is are the uniprot toxin hits.  The coloured lines connecting the right bar to left indicate which hit was most significant for each transcript. (Note:if the bar on the right is completely black in colour, this indicates that there were simply too many transcripts to display. \n\n") 
```
<div> 
### % of Relative kallisto-predicted expression of transcripts with and without uniprot toxin hit (Evalue < 1e^-5)

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
P2 <- readPNG(pie2)
P2 <- grid.raster(P2)
cat("\n\n Figure 7. Pie Chart displaying the kallisto-estimated expression of transcripts with and without a hit to uniprot toxin with an E-value of less than 1e^-5. \n\n ") 
```

### % kallisto-predicted expression of transcripts with and without uniprot toxin hit (BitScore >= 50)

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
P3 <- readPNG(pie3)
P3 <- grid.raster(P3)
cat("\n\n Figure 8. Pie Chart displaying the kallisto-estimated expression of transcripts with and without a hit to uniprot toxin(BitScore\\(\\geq 50\\)). \n\n ") 
```


### Relative kallisto-predicted expression of transcripts with uniprot toxin hit 

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
P4 <- readPNG(pie4P)
P4 <- grid.raster(P4)

P4L <- readPNG(pie4L)
P4L <- grid.raster(P4L)

cat("\n\n Figure 9. Pie Chart showing the relative kallisto-predicted expression of the transcripts with a uniprot toxin hit(BitScore\\(\\geq 50\\)).\n\n") 
```
### Top 10 relatively most expressed unitprot toxin matched transcripts 

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}
Table13 <- read.csv(topkallisto)
Table13 <- Table13[1:10, ]
Table13 %>%
  kable("html", 
        booktabs = TRUE, 
        escape = FALSE) %>%  # Escape = FALSE to render HTML
  kable_styling(bootstrap_options = c("hover", "condensed"), 
                full_width = FALSE, 
                position = "center") %>% 
  column_spec(1, width = "4cm", bold = TRUE, color = "white", background = "black") %>% 
  row_spec(0, bold = TRUE, font_size = 14, color = "white", background = "black")
```

```{r, results='asis', echo=FALSE, align = 'center'}
Table13 %>% 
  download_this(
    output_name = paste0(Sys.Date(), "_Table13. Relative Composition of Transcripts with hits to known toxins_", Name),
    output_extension = ".csv",
    button_label = "Download distinct transcript as csv",
    button_type = "primary",
    csv2 = FALSE,
  )
```

```{r,echo = FALSE, message = FALSE, warning = FALSE, results='asis'}

cat("\n\nTable 1. Top 10 relatively most expressed UniProt toxin-matched transcripts expressed as a percentage of all transcripts with at least one significant UniProt toxin match (BitScore\\(\\geq 50\\)).\n\n")

```

</div>
