---
title: "ORFs Figures"
output: 
  html_document:
    css: style.css 
params:
  kallistotop20graphtransdecoder: NULL
  kallistotop500graphtransdecoder: NULL
  busco_figure1: NULL
  busco_figure2: NULL
  busco_figure3: NULL
  alluvial3P: NULL
  alluvial3L: NULL
  alluvial4P: NULL
  alluvial4L: NULL
  pie5: NULL
  pie6: NULL
  pie7: NULL
  pie8P: NULL
  pie8L: NULL
  topkallisto_transdecoder: NULL
  AuthorName: NULL
  SampleName: NULL

---

<style>
.table-hover > tbody > tr:hover {
  background-color: grey; 
}

caption {
  color: white;
  font-weight: bold;
}


</style>
  
```{r setup, include=FALSE,echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(repos = c(CRAN = "https://cran.rstudio.com"))

```

```{r, echo = FALSE, message=FALSE, warning= FALSE, results = 'hide'}
library(readr)
library(tidyr)
library(knitr)
library(gridExtra)
library(kableExtra)
library(png)
library(grid)
library(DT)
library(kableExtra)
library(downloadthis)
```

```{r}
#load files 
kallistotop20graphtransdecoder <- params$kallistotop20graphtransdecoder
kallistotop500graphtransdecoder <- params$kallistotop500graphtransdecoder
alluvial3P <- params$alluvial3P
alluvial4P <- params$alluvial4P
alluvial3L <- params$alluvial3L
alluvial4L <- params$alluvial4L
pie5 <- params$pie5
pie6 <- params$pie6
pie7 <- params$pie7
pie8P <- params$pie8P
pie8L <- params$pie8L
topkallisto <- params$topkallisto_transdecoder
Sample_Name <- params$SampleName
Name <- params$AuthorName
```
<hr style="border: 1px solid white; width: 100%; margin:0px; padding:0px;" />

<!-- get current date --> 
  `r Sys.Date()` ---
**`r Name`** ---
**`r Sample_Name`** 
<hr style="border: 1px solid white; width: 100%; margin:0px; padding:0px;" />

<div align="center">

### BUSCO 

```{r, results='asis'}
if (nchar(params$busco_figure1) > 0) {
  knitr::include_graphics(params$busco_figure1)
}
```

```{r, results='asis'}
if (nchar(params$busco_figure2) > 0) {
  knitr::include_graphics(params$busco_figure2)
}
```

```{r, results='asis'}
if (nchar(params$busco_figure3) > 0) {
  # Use busco_figure3
  knitr::include_graphics(params$busco_figure3)
}
cat(" \n\n Figure 1. BUSCO score of translatome(s). \n\n ") 

```


### Kallisto Distribution of Top 500 expressed transcripts 

```{r, results='asis'}
Trinity_Top500_read <- readPNG(kallistotop500graphtransdecoder)
top500 <- grid.raster(Trinity_Top500_read)
cat(" \n\n Figure 2. Kallisto Distribution of Top 500 expressed transcripts. Kallisto was run using Transdecoder file as an index and trimmomatic files as inputs with bootstraps.Y axis shows the transcript per million(tpm) counts per target id. X shows each target id (Transdecoder sequence). \n\n ")
```

### Kallisto Distribution of Top 20 expressed transcripts 


```{r, results='asis'}
Trinity_Top200_read <- readPNG(kallistotop20graphtransdecoder)
top200 <- grid.raster(Trinity_Top200_read)
cat(" \n\n Figure 3. Kallisto Distribution of Top 20 expressed transcripts. Kallisto was run using transcoder file as an index and trimmomatic files as inputs with bootstraps. Left Y axis shows the transcript per million(tpm) counts per target id. Right Y axis shows the cumulative percent of expression the top 20 most expressed transcripts. X shows each target id (transcoder sequence). \n\n ")
```

### % of with a significant hit to a unitprot toxin 

```{r, results='asis'}
P1 <- readPNG(pie5)
P1 <- grid.raster(P1)
cat("\n\n Figure 4. Pie chart showing the percentage of Transdecoder transcripts that showed a significant hit to annotated uniprot toxin. Blastp was done using the Transdecoder pep  file as the query and the annotated toxin database from uniprot as the database.Pie chart represents what percentage of distinct trinity transcripts had at least one uniprot toxin match with a BitScore of at least 50. \n\n") 
```


### Most significant uniprot toxin hit per transcript (BitScore >= 50)
<div style="background-color: white; padding: 0px; margin: 0px">

```{r, results='asis'}
knitr::include_graphics(alluvial3P)
knitr::include_graphics(alluvial3L)
```
</div>
```{r, results='asis'}
cat(" \n\n Figure 5. Alluvial graph representing the most significant uniprot toxin hit per transcript with at least one significant uniprot toxin hit. Significance threshold for this graph is a Bitscore of at least 50. On the right is each of the distinct transdecoder transcripts with at least one significant uniprot toxin hit. One the left is are the uniprot toxin hits.  The coloured lines connecting the right bar to left indicate which hit was most significant for each transcript. (Note:if the bar on the right is completely black in colour, this indicates that there were simply too many transcripts to display. \n\n") 
```

### Most significant uniprot toxin hit per transcript (BitScore >= 250)

<div style="background-color: white; padding: 0px; margin: 0px">

```{r, results='asis'}
knitr::include_graphics(alluvial4P)
knitr::include_graphics(alluvial4L)
```
</div>
```{r, results='asis'}

cat("\n\n Figure 6. Alluvial graph representing the most significant uniprot toxin hit per transcript with at least one significant uniprot toxin hit. Significance threshold for this graph is a Bitscore of at least 250. On the right is each of the distinct transdecoder transcripts with at least one significant uniprot toxin hit. One the left is are the uniprot toxin hits.  The coloured lines connecting the right bar to left indicate which hit was most significant for each transcript. (Note:if the bar on the right is completely black in colour, this indicates that there were simply too many transcripts to display. \n\n") 
```

### % of Relative kallisto-predicted expression of transcripts with and without uniprot toxin hit (Evalue < 1e^-5)

```{r, results='asis'}
P2 <- readPNG(pie6)
P2 <- grid.raster(P2)
cat("\n\n Figure 7. Pie Chart displaying the kallisto-estimated expression of transcripts with and without a hit to uniprot toxin with an E-value of less than 1e^-5. \n\n ") 
```

### % kallisto-predicted expression of transcripts with and without uniprot toxin hit (BitScore >= 50)

```{r, results='asis'}
P3 <- readPNG(pie7)
P3 <- grid.raster(P3)
cat("\n\n Figure 8. Pie Chart displaying the kallisto-estimated expression of transcripts with and without a hit to uniprot toxin(BitScore\\(\\geq 50\\)).\n\n ") 
```


### Relative kallisto-predicted expression of transcripts with uniprot toxin hit 
<div style="background-color: white; padding: 0px; margin: 0px">

```{r, results='asis'}

knitr::include_graphics(pie8P)
knitr::include_graphics(pie8L)
```
</div>
```{r, results='asis'}
cat("\n\n Figure 9. Pie Chart showing the relative kallisto-predicted expression of the transcripts with a uniprot toxin hit(BitScore\\(\\geq 50\\)).\n\n") 
```

### Top 10 relatively most expressed unitprot toxin matched transcripts 

```{r, results='asis'}
Table14 <- read.csv(topkallisto)
Table14 <- Table14[1:10, ]
Table14 %>%
  kable("html", 
        booktabs = TRUE, 
        escape = FALSE) %>%  # Escape = FALSE to render HTML
  kable_styling(bootstrap_options = c("hover", "condensed"), 
                full_width = FALSE, 
                position = "center") %>%  
  column_spec(1, width = "4cm", bold = TRUE, color = "white", background = "black") %>% 
  row_spec(0, bold = TRUE, font_size = 14, color = "white", background = "black")
```

```{r, results='asis', echo=FALSE}
Table14 %>% 
  download_this(
    output_name = paste0(Sys.Date(), "_Table14.Transdecoder.Relative Composition of Transcripts with hits to known toxins_", Name),
    output_extension = ".csv",
    button_label = "Download distinct transcript as csv",
    button_type = "primary",
    csv2 = FALSE,
  )
```


```{r, results='asis'}
cat("\n\nTable 1. Top 10 relatively most expressed UniProt toxin-matched transcripts expressed as a percentage of all transcripts with at least one significant UniProt toxin match(BitScore\\(\\geq 50\\)).\n\n")
```

</div>
