---
title: "Transdecoder Figures"
output: 
  html_document:
    css: style.css 
params:
  kallistotop20graphtransdecoder: NULL
  kallistotop500graphtransdecoder: NULL
  busco_figure_transdecoder: NULL
  alluvial3: NULL
  alluvial4: NULL
  pie5: NULL
  pie6: NULL
  pie7: NULL
  pie8: NULL
  topkallisto_transdecoder: NULL
  name: NULL
---
<!-- get current date --> 
**`r params$name`**  
  `r Sys.Date()`
  
  
```{r setup, include=FALSE,echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(repos = c(CRAN = "https://cran.rstudio.com"))

```

```{r, echo = FALSE, message=FALSE, warning= FALSE, results = 'hide'}
library(readr)
library(tidyr)
library(knitr)
library(gridExtra)
library(kableExtra)
library(png)
library(grid)
library(DT)
library(kableExtra)
```

```{r}
#load files 
kallistotop20graphtransdecoder <- params$kallistotop20graphtransdecoder
kallistotop500graphtransdecoder <- params$kallistotop500graphtransdecoder
busco_figure <- params$busco_figure_transdecoder
alluvial3 <- params$alluvial3
alluvial4 <- params$alluvial4
pie5 <- params$pie5
pie6 <- params$pie6
pie7 <- params$pie7
pie8 <- params$pie8
topkallisto <- params$topkallisto_transdecoder
```

### BUSCO transcriptome 

```{r, results='asis'}
busco  <- readPNG(busco_figure)
#plot the busco graph 
busco <- grid.raster(busco)
cat(" \n\n Figure 1. BUSCO score of Translatome against metazoan(met) and molluscan(mol) databases. Y axis shows the results from two different busco assessments using the different databases. X shows the relative distribution of Complete, Duplicated, Fragmented and Missing buncos \n\n ") 
```

### Kallisto Distribution of Top 500 expressed transcripts 

```{r, results='asis'}
Trinity_Top500_read <- readPNG(kallistotop500graphtransdecoder)
top500 <- grid.raster(Trinity_Top500_read)
cat(" \n\n Figure 2. Kallisto Distribution of Top 500 expressed transcripts. Kallisto was run using Transdecoder file as an index and trimmomatic files as inputs with bootstraps.Y axis shows the transcript per million(tpm) counts per target id. X shows each target id (Transdecoder sequence). \n\n ")
```

### Kallisto Distribution of Top 20 expressed transcripts 


```{r, results='asis'}
Trinity_Top200_read <- readPNG(kallistotop20graphtransdecoder)
top200 <- grid.raster(Trinity_Top200_read)
cat(" \n\n Figure 3. Kallisto Distribution of Top 20 expressed transcripts. Kallisto was run using transcoder file as an index and trimmomatic files as inputs with bootstraps. Left Y axis shows the transcript per million(tpm) counts per target id. Right Y axis shows the cumulative percent of expression the top 20 most expressed transcripts. X shows each target id (transcoder sequence). \n\n ")
```

### % of Transdecoder Transcripts with a significant hit to a unitprot toxin

```{r, results='asis'}
P1 <- readPNG(pie5)
P1 <- grid.raster(P1)
cat("\n\n Figure 4. Pie chart showing the percentage of Transdecoder transcripts that showed a significant hit to annotated uniprot toxin. Blastp was done using the Transdecoder pep  file as the query and the annotated toxin database from uniprot as the database. Results were filtered for hits with a BitScore of at least 50. Pie chart represents what percentage of distinct trinity transcripts had at least one uniprot toxin match with a BitScore of at least 50. \n\n") 
```


### Most significant uniprot toxin hit per transcript (BitScore > 50)

```{r, results='asis'}
A1 <- readPNG(alluvial3)
A1 <- grid.raster(A1)
cat(" \n\n Figure 5. Alluvial graph representing the most significant uniprot toxin hit per transcript with at least one significant uniprot toxin hit. Significance threshold for this graph is a Bitscore of at least 50. On the right is each of the distinct transdecoder transcripts with at least one significant uniprot toxin hit. One the left is are the uniprot toxin hits.  The coloured lines connecting the right bar to left indicate which hit was most significant for each transcript. (Note:if the bar on the right is completely black in colour, this indicates that there were simply too many transcripts to display. \n\n") 
```

### Most significant uniprot toxin hit per transcript (BitScore > 300)


```{r, results='asis'}
A2 <- readPNG(alluvial4)
A2 <- grid.raster(A2)
cat("\n\n Figure 6. Alluvial graph representing the most significant uniprot toxin hit per transcript with at least one significant uniprot toxin hit. Significance threshold for this graph is a Bitscore of at least 300. On the right is each of the distinct transdecoder transcripts with at least one significant uniprot toxin hit. One the left is are the uniprot toxin hits.  The coloured lines connecting the right bar to left indicate which hit was most significant for each transcript. (Note:if the bar on the right is completely black in colour, this indicates that there were simply too many transcripts to display. \n\n") 
```

### % of Relative kallisto-predicted expression of transcripts with and without uniprot toxin hit (E-value < 1e-5)

```{r, results='asis'}
P2 <- readPNG(pie6)
P2 <- grid.raster(P2)
cat("\n\n Figure 7. Pie Chart displaying the relative percentage of Kallisto-predicted transcripts with a hit to uniprot toxin with an E-value of less than 1e^-5.\n\n ") 
```

### % kallisto-predicted expression of transcripts with and without uniprot toxin hit (BitScore > 50)

```{r, results='asis'}
P3 <- readPNG(pie7)
P3 <- grid.raster(P3)
cat("\n\n Figure 8. Pie Chart displaying the relative percentage of Kallisto-predicted transcripts with a hit to uniprot toxin with a bitscore of at least 50. \n\n ") 
```


### Relative kallisto-predicted expression of transcripts with uniprot toxin hit (BitScore > 300)

```{r, results='asis'}
P4 <- readPNG(pie8)
P4 <- grid.raster(P4)
cat("\n\n Figure 9. Pie Chart showing the relative kallisto-predicted expression of the transcripts with a uniprot toxin hit of at least 300. \n\n ") 
```

## Top 10 relatively most expressed unitprot toxin matched transcripts 

```{r, results='asis'}
Table4 <- read.csv(topkallisto)
Table4 <- Table4[1:10, ]
Table4 %>%
  kable("html", 
        caption = "Top 10 Uniprot toxin Transcript Expression", 
        booktabs = TRUE, 
        escape = FALSE) %>%  # Escape = FALSE to render HTML
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE, 
                position = "center") %>% 
  column_spec(1, width = "4cm", bold = TRUE, color = "white", background = "#4CAF50") %>% 
  row_spec(0, bold = TRUE, font_size = 14, color = "white", background = "#4CAF50")
cat("\n\n Table1. Top 10 relatively most expressed uniprot toxin matched transcripts expressed a percentage of all transcripts with at least one significant uniprot toxin (BitScore >50)\n\n ") 
```